A NetdiffuseR Tutorial: Estimating Network Influences on Behavior within the Diffusion Paradigm

### 2024-12-05 example.qmd
Final tweaks in the header

---
title: "A NetdiffuseR Tutorial: Estimating Network Influences on Behavior within the Diffusion Paradigm"
format:
  pdf:
    documentclass: apa7
editor: visual
keep-tex: true
author: 
  - name: George G. Vega Yon
  - name: Aníbal L. Olivera M.
  - name: Thomas W. Valente
bibliography: bibliography.bib
---

@@

@@

The workhorse variable used to measure network influences on adoption is network exposure which is the number or proportion of adopters in a person’s immediate social network contemporaneously or lagged by one (or more) time periods (which depending on the study could be days, months, or years). The formula for the lagged exposure model is:
Eit= i ≠jWijaj(t-1)i ≠jWi+                                                                                     (1)

@@

```{r}
#| label: disadoption-example
set.seed(1231)

@@

```{r}
#| label: disadoption example

>>>>

---
title: "A NetdiffuseR Tutorial: Estimating Network Influences on Behavior within the Diffusion Paradigm"
format:
  pdf:
    classoption:
      - twocolumn
keep-tex: true
bibliography: bibliography.bib
author: 
  - name: George G. Vega Yon
    affiliation: University of Utah
  - name: Aníbal L. Olivera M.
    affiliation: Universidad del Desarrollo
  - name: Thomas W. Valente
    affiliation: University of Southern California
# include-in-header: header.tex
---

@@

# Introduction

@@

The workhorse variable used to measure network influences on adoption is network exposure which is the number or proportion of adopters in a person’s immediate social network contemporaneously or lagged by one (or more) time periods (which depending on the study could be days, months, or years). The formula for the lagged exposure model is:

$$
E_{it} = \frac{\sum_{i\neq j}W_{ij}a_{j(t-1)}}{\sum_{i\neq j}W_{i+}}
$$

@@

```{r}
#| label: disadoption-example-1
set.seed(1231)

@@

```{r}
#| label: disadoption-example-2
